Case study validations of automatic bullet matching

### 2018-11-27 index.Rmd
Cite press release for sensofar

Note that the sequence average maximum of the correlation between lands is used in SensoComp \hh{citation for that?}\svp{It's your claim... I looked for a citation and didn't find one. Closed-source proprietary = no references?} to capture the similarity between bullets. The correlation based SAM score has also been called the 'average correlation calculated at the max phase' in \citet{chuPilotStudyAutomated2010}.

>>>>

Note that the sequence average maximum of the correlation between lands is used in SensoComp \citep{sensofar-sam} to capture the similarity between bullets. The correlation based SAM score has also been called the 'average correlation calculated at the max phase' in \citet{chuPilotStudyAutomated2010}.
